The Astropy Project

### 2017-10-04 main.tex
edits to jpl ephemerides bit

\subsubsection{Overview}
The \package{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \package{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects. Some of the machinery also relies on the Essential Routines of Fundamental Astronomy (ERFA) C library for some of the critical underlying transformation machinery.
\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as spherical (right ascension, declination, and distance from solar system barycenter) or Cartesian coordinates ($x$, $y$, $z$ with the origin at ).
They can therefore change representations independent of being transformed to other reference frames (e.g., the Galactic coordinate frame).

@@

    \item[Solar System Ephemerides]
    \comment{EJT}{APW, you may want to give this item a quick read-over?  If it looks good just delete this comment}
    Also new is support for computing ephemeris of major solar system bodies and outputting the resulting positions as coordinate objects. 
    These ephemerides can be computed either using analytic approximations from ERFA (which requires no data download beyond the source code), or from downloaded JPL ephemerides (which requires the \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}} optional dependency). 
    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide the gateway to this functionality, yielding \texttt{SkyCoord} objects given a specific body and choice of ephemeris source.

>>>>

\subsubsection{Overview}
The \package{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \package{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
Some of the machinery also relies on the Essential Routines of Fundamental
Astronomy (ERFA) \texttt{C} library for some of the critical underlying
transformation machinery.
\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as spherical (right
ascension, declination, and distance from solar system barycenter) or Cartesian
coordinates ($x$, $y$, $z$ with the origin at ).
They can therefore change representations independent of being transformed to
other reference frames (e.g., the Galactic coordinate frame).

@@

    \item[Solar System Ephemerides]
    Also new is support for computing ephemerides of major solar system bodies
    and outputting the resulting positions as coordinate objects.
    These ephemerides can be computed either using analytic approximations from
    ERFA, or from downloaded JPL ephemerides (the latter requires the \package{j
    plephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
    optional dependency and an internet connection).
    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
    the gateway to this functionality, yielding \texttt{SkyCoord} objects given
    a specific body and choice of ephemeris source.
